---
title: "<b>MIDTERM PROJECT</b>"
author: "<br>Andrew Sisitzky,Chen Xu<br>Guangze Yu,Yuyang Li"
date: "<br>2021 November 1"
output: 
  revealjs::revealjs_presentation:
    #template: hw_temp_1.html
    theme: sky
    highlight: pygments 
    #css: reveal.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("tidyverse","ggplot2","dplyr", "maps", "treemapify")
source("ultimate data wrangle and clean.R", echo=TRUE)
source("visualization function midterm.R", echo=TRUE)
```




# 

<div style= "align:center; font-size:80px;">
<p><br><br><b>
DATA WRANGLING 
</b>
</p>

</div>


## Data clean-Strawberries.csv
 - Take apart strawberries.csv and restructure.
 - Use <i><b>Year, State, Domain, Chemical, Chemical type, Value, units </i></b>as variable to get a new table.
 
 - Select data when<i><b> Domain = "CHEMICAL"</i></b>.
 
## Data clean-Strawberries.csv

 - Empty rows were removed to make the data more compact.
 
 - The name of various pesticides were converted to uppercase letters for later matching.

## Data wrangling-left_join

 - Function <i>left_join</i> is used to match the data by <i><b>"chemicaltype = pesticide" </i></b> .
 
 - Combine them into one table for subsequent EDA.
 
 - Delete the missing value if <i><b>"Year = NA"</i></b>.


</section>

# 
<div style= "align:center; font-size:80px;">
<p><br><br><b>
MAKE JUDGEMENTS
</b>
</p>

</div>


## Give a number for toxins

 - <b>For human</b>
<div><br>
<table><tbody>
<tr>
<th style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Chemical\Level</th>
<th style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">1</th>
<th style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">2</th>
<th style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);">3</th>
<th style="padding: 3px; border-color: rgb(0, 0, 0);">4</th>
</tr>
<tr>
<td style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Carcinogen:</td>
<td style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">unknown</td>
<td style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">possible</td>
<td style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);">probable</td>
<td style="padding: 3px; border-color: rgb(0, 0, 0);">known</td>
</tr>
<tr>
<td style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Hormone.Disruptor</td>
<td style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">unknown</td>
<td style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">suspected</td>
<td style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);"></td>
<td style="padding: 3px; border-color: rgb(0, 0, 0);"></td>
</tr>
<tr>
<td style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Hormone.Disruptor</td>
<td style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">unknown</td>
<td style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">present</td>
<td style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);"></td>
<td style="padding: 3px; border-color: rgb(0, 0, 0);"></td>
</tr>
<tr>
<td style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Developmental/Reproductive Toxins</td>
<td style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">unknown</td>
<td style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">present</td>
<td style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);"></td>
<td style="padding: 3px; border-color: rgb(0, 0, 0);"></td>
</tr>
</tbody></table><br></div>


 -  <b>For bee</b>
 <div><br>
<table><tbody>
<tr>
<th style="width: 259px; padding: 3px;">Chemical\Level</th>
<th style="padding: 3px;">1</th>
<th style="padding: 3px;">2</th>
<th style="padding: 3px;">3</th>
<th style="padding: 3px;">4</th>
</tr>
<tr>
<td style="width: 259px; padding: 3px;">Bee.Toxins</td>
<td style="padding: 3px;">unknown</td>
<td style="padding: 3px;">slight</td>
<td style="padding: 3px;">moderate</td>
<td style="padding: 3px;">high</td>
</tr>
</tbody></table></div>


## Calculate total toxins
 -  <b>For human</b>
 
    + Toxicity for human = <i>Carcinogen+HormoneDisruptor+Neurotoxins+ Developmental or Reproductive Toxins</i>
     
 -  <b>For bee</b>
 
    + Toxicity for bee = <i>Bee.Toxins</i>  
  


</section>

# 
<div style= "align:center; font-size:80px;">
<p><br><br><b>
Topic we study
</b>
</p>

</div>
 - How the human-harm pesticide usage differ as time passes in the major strawberries producing areas in the US.
</section>

# 

<div style= "align:center; font-size:80px;">
<p><br><br><b>
EDA
</b>
</p>

</div>


## Choose data to plot

 - Select chemical types exist in <i><b>Pesticides.csv</i></b>.
 
 - Filter dataframe into subsets in different measurements.
    + MEASURED IN LB / ACRE / YEAR  AVG
    + MEASURED IN PCT OF AREA BEARING  AVG
    + MEASURED IN LB
    + MEASURED IN LB / ACRE / APPLICATION  AVG
    + MEASURED IN NUMBER  AVG
  - We chose subset of <b>MEASURED IN LB</b> for later analysis.

## Map of mean toxicity for human

 - Created a map to visualize the mean toxicity for each state.


 - Took data across all years, calculated the means, and plotted the results on a map of the United States.
 
 
## The map:

```{r,echo=FALSE}
map_function(eda_subset)
```

## Conclusion of map
 - We found that California and Florida on average had lower human toxicity levels than Washington and Oregon.
 
 - This plot shows that, based on this dataset, the harvests in Oregon tended to use chemicals that were rated higher by our toxicity scale in comparison to other states.


## Pesticides frequency

 - For the first plot, we focused on frequency of total pesticides across 3 years. 
 
 -  For the second plot, we looked at each chemical type and plotted its frequency of usage across 3 years.
 
 
## Total Pesticides frequency <br>2016 vs. 2018 vs. 2019
```{r,echo=FALSE}
chemcialtype_freq_barchart_function(chemicaltype_freq)
```

## Separate Pesticides frequency <br>2016 vs. 2018 vs. 2019
```{r,echo=FALSE}
chemicaltype_freq_function(chemicaltype_freq)
```

## Conclusion of pesticides frequency
 - We find that the amount of chemical be used across the 3 years decreased.
 
 - Now as we know the specific usage of each chemical type through 3 years. We want to dive deeper into the distribution of toxicity level that related to human for each year.

## Frequency of 5 toxicity levels for human
 - Dive deeper into the distribution of toxicity level that related to human for each year.
 
 - Using the toxicity levels we defined before. 

## Frequency 2016
```{r,echo=FALSE}
human_toxicity_level_function(year1_toxicityhuman_freq) + ggtitle("Pesticide Toxicitylevelhuman Frequency 2016")
```


## Frequency 2018
```{r,echo=FALSE}
human_toxicity_level_function(year2_toxicityhuman_freq) + ggtitle("Pesticide Toxicitylevelhuman Frequency 2018")
```

## Frequency 2019
```{r,echo=FALSE}
human_toxicity_level_function(year3_toxicityhuman_freq) + ggtitle("Pesticide Toxicitylevelhuman Frequency 2019")
```

## Conclusion for EDA and our posed project topic:
 - After we view all the three plots about the distribution, we conclude that althought the total amount of chemical be used across the 3 years decreased, the propotion of toxicitylevel remains relatively the same.
 
 - We can say that even though the amount of chemicals they are treating the strawberries with is decreasing, those that they are using are still known to be toxic to humans.

</section>



