---
title: "MIDTERM PROJECT"
author: "Andrew Sisitzky,Chen Xu,Guangze Yu,Yuyang Li"
date: "20201 November 1"
output: 
  revealjs::revealjs_presentation:
    #template: hw_temp_1.html
    theme: sky
    highlight: pygments 
    #css: reveal.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("tidyverse","ggplot2","dplyr", "maps", "treemapify")
source("ultimate data wrangle and clean.R", echo=TRUE)
source("visualization function midterm.R", echo=TRUE)
```




# 

<div style= "align:center; font-size:80px;">
<p><br><br><b>
DATA WRANGLING 
</b>
</p>

</div>


## Data clean-Strawberries.csv
 - Take apart strawberries.csv and restructure, 
 - Use <i><b>Year, State, Domain, Chemical, Chemical type, Value, units </i></b>as variable to get a new table
 
 - Select data when<i><b> Domain = "CHEMICAL"</i></b>
 
## Data clean-Strawberries.csv

 - Empty rows were removed to make the data more compact
 
 - The name of various pesticides were converted to uppercase letters for later matching

## Data wrangling-left_join

 - Function <i>left_join</i> is used to match the data by <i><b>"chemicaltype = pesticide" </i></b> 
 
 - Combine them into one table for subsequent EDA
 
 - Delete the missing value if <i><b>"Year = NA"</i></b>


</section>

# 
<div style= "align:center; font-size:80px;">
<p><br><br><b>
MAKE JUDGEMENTS
</b>
</p>

</div>


## Give a number for toxins

 - <b>For human</b>
<div><br>
<table><tbody>
<tr>
<th style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Chemical\Level</th>
<th style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">1</th>
<th style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">2</th>
<th style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);">3</th>
<th style="padding: 3px; border-color: rgb(0, 0, 0);">4</th>
</tr>
<tr>
<td style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Carcinogen:</td>
<td style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">unknown</td>
<td style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">possible</td>
<td style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);">probable</td>
<td style="padding: 3px; border-color: rgb(0, 0, 0);">known</td>
</tr>
<tr>
<td style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Hormone.Disruptor</td>
<td style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">unknown</td>
<td style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">suspected</td>
<td style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);"></td>
<td style="padding: 3px; border-color: rgb(0, 0, 0);"></td>
</tr>
<tr>
<td style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Hormone.Disruptor</td>
<td style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">unknown</td>
<td style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">present</td>
<td style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);"></td>
<td style="padding: 3px; border-color: rgb(0, 0, 0);"></td>
</tr>
<tr>
<td style="width: 344px; padding: 3px; border-color: rgb(0, 0, 0);">Developmental/Reproductive Toxins</td>
<td style="width: 151px; padding: 3px; border-color: rgb(0, 0, 0);">unknown</td>
<td style="width: 156px; padding: 3px; border-color: rgb(0, 0, 0);">present</td>
<td style="width: 155px; padding: 3px; border-color: rgb(0, 0, 0);"></td>
<td style="padding: 3px; border-color: rgb(0, 0, 0);"></td>
</tr>
</tbody></table><br></div>


 -  <b>For bee</b>
 <div><br>
<table><tbody>
<tr>
<th style="width: 259px; padding: 3px;">Chemical\Level</th>
<th style="padding: 3px;">1</th>
<th style="padding: 3px;">2</th>
<th style="padding: 3px;">3</th>
<th style="padding: 3px;">4</th>
</tr>
<tr>
<td style="width: 259px; padding: 3px;">Bee.Toxins</td>
<td style="padding: 3px;">unknown</td>
<td style="padding: 3px;">slight</td>
<td style="padding: 3px;">moderate</td>
<td style="padding: 3px;">high</td>
</tr>
</tbody></table></div>


## Calculate total toxins
 -  <b>For human</b>
 
    + Toxicity for human = <i>Carcinogen+HormoneDisruptor+Neurotoxins+ Developmental or Reproductive Toxins</i>
     
 -  <b>For bee</b>
 
    + Toxicity for bee = <i>Bee.Toxins</i>  
  


</section>

# 

<div style= "align:center; font-size:80px;">
<p><br><br><b>
EDA
</b>
</p>

</div>


## Choose data to plot

 - Select chemical types exist in <i><b>Pesticides.csv</i></b>
 
 - Filter dataframe into subsets in different measurements
    + MEASURED IN LB / ACRE / YEAR  AVG
    + MEASURED IN PCT OF AREA BEARING  AVG
    + MEASURED IN LB
    + MEASURED IN LB / ACRE / APPLICATION  AVG
    + MEASURED IN NUMBER  AVG

## The map for major strawberry producing area in the US(including the mean toxicity level for human)

 - Looking at the average lbs of strawberries harvested per acre in each state.Added color to show the toxicity level of each observation. 
 
 - It appears that the harvests with higher lbs per acre also tend to be treated with chemicals that are rated higher by out <i><b>'toxicitylevelhuman'</i></b> variable.
 
 
## The map:

```{r}
map_function(eda_subset)
```


## Total Pesticide usage: 2016 vs. 2018 vs. 2019

 - Adding the <b>mean toxicity</b> of all observations in each state to the map.  
 
 - This plot shows that, based on this dataset, the harvests in Oregon tended to use chemicals that were rated higher by our toxicity scale in comparison to other states.
 
## Total Pesticide usage: 2016 vs. 2018 vs. 2019 plot
```{r}
chemcialtype_freq_barchart_function(chemicaltype_freq)
```


## Comparison of Pesdicide usage: 2016 vs. 2018 vs. 2019
```{r}
chemicaltype_freq_function(chemicaltype_freq)
```

## Pesticide Toxicitylevelhuman Frequency 2016
```{r}
human_toxicity_level_function(year1_toxicityhuman_freq) + ggtitle("Pesticide Toxicitylevelhuman Frequency 2016")
```


## Pesticide Toxicitylevelhuman Frequency 2018
```{r}
human_toxicity_level_function(year2_toxicityhuman_freq) + ggtitle("Pesticide Toxicitylevelhuman Frequency 2018")
```

## Pesticide Toxicitylevelhuman Frequency 2019
```{r}
human_toxicity_level_function(year3_toxicityhuman_freq) + ggtitle("Pesticide Toxicitylevelhuman Frequency 2019")
```




</section>



